Local PCA Shows How Population Structure Differs Along the Genome

### 2016-06-17 writeup/local_pca_paper.tex
update

>>>>

\begin{figure}
    \begin{center}
       \includegraphics[width=1\textwidth]{MDS_1D_win100_all_chr_col_by_chr_with_legend}
    \end{center}
    \caption{
        MDS 1D plot along all 22 autosomes in Human.
        \label{fig:mds1_along_allchr_human}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.85\textwidth]{FigS_Together_MDS_plot_allchr}
    \end{center}
    \caption{
        MDS plots for all 8 chromosomes in \textit{Medicago truncatula}.
        \label{fig:mds_medicago_allchr}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.8\textwidth]{FigS_pca_plots_for_Medicago_allchr_3peaks_byMDS}
    \end{center}
    \caption{
        PCA plots for all 8 chromosomes' 3 peaks in \textit{Medicago truncatula}.
        \label{fig:pca_peaks_medicago_allchr}
    }
\end{figure}
